Cost of Living in Toronto

### 2024-09-21 paper/paper.qmd
fixed

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Cost of Living in Toronto"
subtitle: "low-income families can not "
author: 
  - Hyunje Park
thanks: "Code and data are available at: https://github.com/davidpxrk/cost-of-living-toronto"
date: today
date-format: long
abstract: "In summary, all the t."
format: pdf
number-sections: true
bibliography: references.bib
---
